The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-18 dit-paper_ieee.tex
Close #19

The general problem of redundancy of a new linear constraint $C \, X \leq d$ w.r.t. a set of previous linear constraints $A \, X \leq B$ in an ILP can itself be written as the ILP presented in Fig.~\ref{fig:redILP}.

@@

Such a linear problem can be solved by e.g. the simplex algorithm and a branch-and-cut approach. However, in our case the problem is not exactly the same as we have a set of constraints and we want to find all redundant constraints within. A naive method would be to test each constraint against all the others. We present a similar method with an efficient preprocessing when most constraints are redundant in Algorithm \ref{alg:prunRedun}.

\begin{algorithm}
\caption{Removing redundancy from CSPACE}
\label{alg:prunRedun}
  \begin{algorithmic}[1]
    \STATE $CSPACE$ : set of constraints
    \STATE $S \leftarrow \emptyset$
    \STATE \COMMENT{$1^{st}$ pass: test each $cstr$ against previous ones}
    \FOR{$cstr$ \textbf{in} $CSPACE$}
      \IF {$cstr$ is not redundant w.r.t. $S$}
        \STATE $S \leftarrow cstr$
      \ENDIF
    \ENDFOR
    \STATE \COMMENT{$2^{nd}$ pass: test each $cstr$ against every other}
    \FOR{$cstr$ \textbf{in} $S$}
      \STATE Remove $cstr$ from $S$
      \IF {$cstr$ is not redundant w.r.t. $S$}
        \STATE Put $cstr$ back into $S$
      \ENDIF
    \ENDFOR
    \RETURN{S}
  \end{algorithmic}
\end{algorithm}

>>>>

Previous sections give us a list of (integer) linear constraints accurately describing the C-space, composed of the DBF test applied to the required intervals. We now give a method to remove redundant constraints from this list.

The general problem of redundancy of some linear constraint $C \, X \leq d$ w.r.t. a set of previous linear constraints $A \, X \leq B$ in an ILP can itself be written as the ILP presented in Fig.~\ref{fig:redILP}.

@@

Such a linear problem can be solved by e.g. the simplex algorithm and a branch-and-cut approach. However, in our case the problem is not to test for redundancy of a particular constraint but to find all redundant constraints within a set. A naive method would be to test every constraint against all the others. We present a similar method with an efficient preprocessing when most constraints are redundant in Algorithm \ref{alg:prunRedun}.

\begin{algorithm}
\caption{Removing redundancy from CSPACE}
\label{alg:prunRedun}
  \begin{algorithmic}[1]
    \STATE $CSPACE$ : set of constraints
    \STATE $S \leftarrow \emptyset$
    \STATE \COMMENT{$1^{st}$ pass: test each $cstr$ against previous ones}
    \FOR{$cstr$ \textbf{in} $CSPACE$}
      \IF {$cstr$ is not redundant w.r.t. $S$}
        \STATE $S.push(cst)rcl$
      \ENDIF
    \ENDFOR
    \STATE \COMMENT{$2^{nd}$ pass: test remaining $cstr$ against every other}
    \FOR{$cstr$ \textbf{in} $S$}
      \STATE $cstr$ = $S.pop()$
      \IF {$cstr$ is not redundant w.r.t. $S$}
        \STATE $S.push(cstr)$
      \ENDIF
    \ENDFOR
    \RETURN{S}
  \end{algorithmic}
\end{algorithm}
